Analytics Without Tuning Considered Harmful?

### 2015-08-12 tuningpredictor.tex
Updates from ShareLaTeX

\wei{added HERE!} As shown in \tab{parameters}, default parameters for the Where-based learner are set using authors' engineering judgment and default parameters for CART and Random Forests are set by SciKitLearn. Those default parameters might not be the standard parameters for practical defect learners in reality, but it's a rule of thumb that most researchers would use just use the default parameters in the software without changes\cite{me07b} (\wei{MORE references should be cited here to support this statement}. )The tuning range is set according to the corresponding default parameters. The reason for this is to tell whether tuning with a small range can get a performance improvement (\Menzies{is this correct?})

@@

\subsection{RQ2:  Does Tuning Change a Learner's Ranking Regarding Different Goals?}\label{sect:rank}
Researchers often use performance criteria to assert that one learner is better than another~\cite{lessmann2008benchmarking,me07b}. In\cite{me07b}, naive Bayes does better than C4.5 in terms of pd and balance over NASA MDP data sets. In \cite{lessmann2008benchmarking}, Random Forest is considered to be statistically better than CART in terms of the AUC ranking. Such conclusions are not reliable since they can change when we elect to tune for different goals.

@@

@@

\begin{figure}[!b]
\includegraphics[width=3.5in,left]{np_10_90.eps}
\caption{Deltas in terms of F when using 10 and 90 as the population in DE. np=90 is better when the deltas are above zero.}\label{fig:deltas_np}
 \end{figure}

@@

\wei{added!} To justify that {\em np=10} is enough, we did another tuning study, 
where all the settings are the same as before but we chose {\em np=90} as recommended by Storn. 
The tuning performance of learners is evaluated
by F. To compare the results of {\em np=10} and {\em np=90}, we plot the delta in the performance as \fig{deltas}. In \fig{deltas_np}, 5 data sets are better but 4 data sets are worse when {\em np = 90} for WHERE. For CART and Random Forest, the numbers of better and worse data sets are both 4. The improvement for those better data sets is negligible to some extent but the deterioration is not. From this study, {\em np = 90}, which is recommended for WHERE and more than the number for CART and Random Forest, does not bring any significant improvement over {\em np=10}. Therefore, the searching space is very simple for tuning defect predictor, which makes tuning very simple.

>>>>

As shown in \tab{parameters}, default parameters for the Where-based learner are set using authors' engineering judgment and default parameters for CART and Random Forests are set by SciKitLearn. Those default parameters might not be the standard parameters for practical defect learners in reality, but it's a rule of thumb that most researchers would use just use the default parameters in the software without any tuning\cite{me07b,moser2008comparative,herzig2013predicting,zimmermann2007predicting}. The tuning range is set according to the corresponding default parameters. The reason for this is to justify whether tuning with a small range can get a performance improvement (\Menzies{is this correct?})

@@

\subsection{RQ2:  Does Tuning Change a Learner's Ranking ?}\label{sect:rank}
Researchers often use performance criteria to assert that one learner is better than another~\cite{lessmann2008benchmarking,me07b}. In\cite{me07b}, naive Bayes does better than C4.5 in terms of pd and balance over NASA MDP data sets. In \cite{lessmann2008benchmarking}, Random Forest is considered to be statistically better than CART in terms of the AUC ranking. Such conclusions are not reliable since they can change when we elect to tune for different goals.

@@

\begin{figure}[!t]
\begin{center}
\includegraphics[width=1.5in]{LR_untuned.eps}\includegraphics[width=1.5in]{LR_tuned.eps}
 \end{center}
\caption{Comparison between tuned and naive SVM learners with rbf and sigmoid kernels over the goal of F. }\label{fig:svm}
 \end{figure}

% \begin{figure}[!t]
% \begin{center}
% \includegraphics[width=1.5in]{svm_rbf.eps}\includegraphics[width=1.5in]{svm_sigmoid.eps}
%  \end{center}
% \caption{Comparison between tuned and naive SVM learners with rbf and sigmoid kernels over the goal of F. }\label{fig:svm}
%  \end{figure}

@@

\begin{figure}[!b]
\begin{center}
\includegraphics[width=1.5in]{np_precision.eps}\includegraphics[width=1.5in]{np_f.eps}
 \end{center}
\caption{Deltas in performance between {\em np = 10} and the recommended np's. The recommended np is better when deltas are above zero. {\em np = 90, 50 and 60} are recommended population size for WHERE, CART and Random Forest by Storn.}\label{fig:deltas_np}
 \end{figure}

@@

To justify that {\em np=10} is enough, we did another tuning study, 
where all the settings were the same as before but we set{\em np= 90, 50} and {\em np = 60} for WHERE, CART and Random Forests as recommended by Storn. The tuning performance of learners was evaluated
by precision and F. To compare performance of each learner with different np's, we plot the delta in the performance as \fig{deltas}. As shown in \fig{deltas_np}, in terms of precision, the recommended {\em np} will improve the performance of WHERE, CART and Random Forests in 2, 5, and 4 data sets. However, in 6, 4, and 4 data sets, those numbers  will degrade the performance compared with {\em np = 10}. For F as the tuning goal, we can observe the similar pattern.

 From this study, with the same experimental condition, the recommended {\em np's} for WHERE, CART and Random Forest, do not bring any significant improvements over {\em np = 10}. We're not arguing that {\em np = 10} is the optimal settings for tuning defect predictors. But it suffices to make tuning easy and generate a competitive performance.
